A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2022-12-02 main.tex
added changes
cover letter added
wrapping up

\usepackage{listings, listings-rust}
\lstset{escapeinside={<@}{@>}}
\usepackage{tabularx}
\usepackage{array}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{graphs} 
\usetikzlibrary{matrix}
\usepackage{multirow}
% \usepackage[backend=bibtex, style=authoryear]{apa}
\usepackage{natbib}
% \addbibresource{bibtex.bib}
\usepackage{todonotes}
\usepackage{hyperref}
\usepackage{subfiles} % Best loaded last in the preamble
\input{defs}

@@

\title{A Study of Common Bug Fix Patterns in Rust%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{}

%\titlerunning{Short form of title}        % if too long for running head

\author{Mohammad Robati Shirzad         \and
        Patrick~Lam %etc.
}

@@

\institute{Mohammad Robati Shirzad \at
              200 University Ave W, Waterloo, ON N2L 3G1 \\
              \email{mrobatis@uwaterloo.ca}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Patrick Lam \at
                200 University Ave W, Waterloo, ON N2L 3G1 \\
                \email{patrick.lam@uwaterloo.ca}
}

@@

\section{Appendix}
\subfile{appendix}

>>>>

\usepackage{listings, listings-rust}
\lstset{escapeinside={<@}{@>}}
\usepackage{tabularx}
\usepackage{array}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{graphs} 
\usetikzlibrary{matrix}
\usepackage{multirow}
% \usepackage[backend=bibtex, style=authoryear]{apa}
\usepackage{natbib}
% \addbibresource{bibtex.bib}
\usepackage{todonotes}
\usepackage{hyperref}
\usepackage{subfiles} % Best loaded last in the preamble
\usepackage{xcolor}
\usepackage{fontawesome5}
\input{defs}

@@

\title{A Study of Common Bug Fix Patterns in Rust
\thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}
}
\subtitle{}
\definecolor{orcidlogocol}{rgb}{0.65, 0.807, 0.223}
\newcommand{\orcid}[1]{$\,$\href{https://orcid.org/#1}{\textcolor{orcidlogocol}{\faOrcid}}}

%\titlerunning{Short form of title}        % if too long for running head
\author{Mohammad Robati Shirzad \orcid{0000-0002-6297-8229}       \and
        Patrick~Lam \orcid{0000-0001-8278-5400} %etc.
}

@@

\institute{Mohammad Robati Shirzad \at
              200 University Ave W, Waterloo, ON N2L 3G1 \\
              \email{mrobatis@uwaterloo.ca}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
}

@@
